### 2020-02-10 submission/cv_models.tex
figures updated, minor text changes

%Recall the differences---in particular, the number of residual connections---between the VGG, ResNet, and DenseNet architectures.
%VGG, while a fine model in many ways, was limited by needing massive FC layers at the end of the model, requiring significant memory and computational resources, and it's poor conditioning led to problems with vanishing gradients.  
%The empirical manifestations of this (on weight matrices) are that fitted $\alpha$ values get much worse for deeper layers.
%%\ncyan{
We can interpret these observations by recalling the architectural differences between the VGG, ResNet, and DenseNet architectures,
and, in particular, the number of of residual connections. VGG resembles the  traditional convolutional architectures,
such as LeNet5, and consists of several [Conv2D-Maxpool-ReLu] blocks, followed by 3 large Fully Connected (FC) layers.
ResNet greatly improved on VGG by replacing the large FC layers, shrinking the Conv2D blocks, and introducing \emph{residual connections}.
This optimized approach allows for greater accurary with far fewer parameters (and GPU memory requirements), and
ResNet models of up to 1000 layers have been trained.\cite{resnet1000}.
%%}
We conjuecture that the effeciency and effectivness of ResNet is reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and strongly optimized.
Contrast this with the DenseNet models, which contains many connections between every layer.
Our results (large $\alpha$, meaning they even a HT model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly optimized.

>>>>

%Recall the differences---in particular, the number of residual connections---between the VGG, ResNet, and DenseNet architectures.
%VGG, while a fine model in many ways, was limited by needing massive FC layers at the end of the model, requiring significant memory and computational resources, and it's poor conditioning led to problems with vanishing gradients.  
%The empirical manifestations of this (on weight matrices) are that fitted $\alpha$ values get much worse for deeper layers.
%%\ncyan{
\paragraph{Comparison of VGG, ResNet, and DenseNet Architectures.}
We can interpret these observations by recalling the architectural differences between the VGG, ResNet, and DenseNet architectures,
and, in particular, the number of of residual connections. VGG resembles the  traditional convolutional architectures,
such as LeNet5, and consists of several [Conv2D-Maxpool-ReLu] blocks, followed by 3 large Fully Connected (FC) layers.
ResNet greatly improved on VGG by replacing the large FC layers, shrinking the Conv2D blocks, and introducing \emph{residual connections}.
This optimized approach allows for greater accurary with far fewer parameters (and GPU memory requirements), and
ResNet models of up to 1000 layers have been trained.\cite{resnet1000}.
%%}
We conjuecture that the effeciency and effectivness of ResNet is reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and strongly optimized.
Contrast this with the DenseNet models, which contains many connections between every layer.
Our results (large $\alpha$, meaning they even a HT model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly optimized.

### 2020-02-10 submission/introduction.tex
figures updated, minor text changes

To answer this question, we analyze hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models, i.e., they can be used to discriminate between ``good-better-best'' models.
However, they can qualitatively fail for models that may not be well-trained, i.e., to distinguish ``good-versus-bad''~models.
\item 
PL-based metrics do much better at predicting quality trends in CV/NLP models---quantitatively better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
PL-based metrics can also be used to characterize fine-scale model properties (including layer-wise \emph{Correlation Flow} and \emph{Scale Collapse} in poorly-trained models) and evaluate post-training modifications (such as model distillation, increasing the dataset size, and other model improvements).
\end{itemize}

>>>>

To answer this question, we analyze hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
%, i.e., they can be used to discriminate between ``good-better-best'' models.
\item
However, norm-based meterics may fail for poorly-trained well-trained, i.e., to distinguish ``good-versus-bad''~models.
\item 
PL-based metrics do much bette--quanttiatviely--at predicting quality trends in pretrained models%---quantitatively better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
PL-based metrics can be used to characterize fine-scale model properties (including layer-wise \emph{Correlation Flow} and \emph{Scale Collapse} in poorly-trained models) and model enhancements (i.e. distillation, finetuning, etc.)
\end{itemize}
